Thermodynamic fragments in magic state theories

### 2021-01-12 magic_paper.tex
simplified/corrected expressions

Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
The computational basis now coincides with the Hamiltonian eigenbasis.
We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}. \ddd{[Completely vital. What Hamiltonian are you choosing? Note you can choose it to make life easy for yourself. E.g. $H=Z$ for example.]}\nick{$X, Z$ are not Hermitian. Currently a general Hamiltonian with spectrum $(\epsilon_0,\epsilon_1,\epsilon_2)$.}
The Wigner distribution of any thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
and always consists of strictly positive components, so pre-order $\prec_{\gamma_\beta}$ is well defined.

>>>>

Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
The computational basis now coincides with the Hamiltonian eigenbasis.
We denote the thermal state at temperature $\beta^{-1}$ by $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.
Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}.

Consider a general qutrit Hamiltonian $H$ with spectrum $(E_0, E_1, E_2)$.
The Wigner distribution of any qutrit thermal state $\gamma_\beta$ is calculated directly by the definition in~\cref{eq:wstate},
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta E_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
and always consists of strictly positive components, therefore the pre-order $\prec_{\gamma_\beta}$ is well defined.

Consider the simple scenario, where $H$ has the spectrum $(1,0,0)$.
Then, $\Z_\beta = 2 + e^{-\beta}$ and the 1-copy Wigner distributions are depicted in~\cref{tab:thermal_w}.
\begin{table}[h]
  \def\arraystretch{2}
  \centering
  \begin{tabular}{c|c|c|c}
    $\bmx = (x_0, x_1)$ & $W_{\noisys}(\bmx)$ & $W_{\gamma_\beta}(\bmx)$ & $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ \\
    \hline
    \makecell{$(0,0)$ \\ \vdots \\ $(0,2)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(1+2e^\beta)}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(1+2e^\beta)$ \\
    \hline
    \makecell{$(1,0)$ \\ $\vdots$ \\ $(2,1)$} & $\displaystyle \frac{1}{6} - \frac{1}{18}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{ -\beta})}$ & $\displaystyle \left(\frac{1}{2}-\frac{1}{6}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
    $(2,2)$ & $\displaystyle -\frac{1}{3} + \frac{4}{9}\epsilon$ & $\displaystyle \frac{1}{3(2+e^{-\beta})}$ & $\displaystyle \left(-1 + \frac{4}{3}\epsilon \right)(2+e^{-\beta})$ \\
    \hline
  \end{tabular}
  \caption{Wigner components $W_{\gamma_\beta}(\bmx)$, $W_{\noisys}(\bmx)$ and their ratio $W_{\noisys}(\bmx)/W_{\gamma_\beta}(\bmx)$ listed in order of decreasing ratio (holds for all $\beta$).}
  \label{tab:thermal_w}
\end{table}
To construct the Lorenz curves, we simply take the cumulative sum of the Wigner components in order of increasing ratio.
